### 2020-06-01 writeup/experiments.tex
sec 1
sec 3

\textbf{Covariate shift.}
We validate that the performance of aligning task covariances depends on the size of source task data.
In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant as we increase the size of the source task dataset.

\begin{figure}[!t]
	\centering
		\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_sst_trec_lstm.pdf}
		\caption{Data size}
		\label{fig_ab_data}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{Covariate shift}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{The performance of aligning task covariances depends on data size. As the ratio between source task data size and target task data size increases, the performance improvement from aligning task covariances increases.}
	\label{fig_ablation}
\end{figure}

>>>>

\textbf{Covariate shift.}
Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
When the source task data size is particularly large compared to the target task, then we expect that applying the covariance alignment algorithm results in a more significant gain.
We validate that the performance of aligning task covariances depends on the size of source task data.
In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant as we increase the size of the source task dataset.

\begin{figure}[!t]
	\centering
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/task_sim_norm_lstm.pdf}
		\caption{Task model}
		\label{fig_ab_sim}
	\end{subfigure}%
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_norm_sst_trec_lstm.pdf}
		\caption{Data size}
		\label{fig_ab_data}
	\end{subfigure}
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.975\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{Covariate shift}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{The performance of aligning task covariances depends on data size. As the ratio between source task data size and target task data size increases, the performance improvement from aligning task covariances increases.}
	\label{fig_ablation}
\end{figure}
